### 2013-10-31 research/paper/figure/m_star_collapsed.tex
uploaded 31 OCt 2013

\setlength{\unitlength}{\textwidth}
\fbox{
  \begin{picture}(1,0.3)(0.0,0.45)

@@

  \end{picture}
  }

  \caption{Mean power as a function of damping factor. Data are presented at $m^*=10$ (\ding{108}), $m^*=20$ (\ding{83}), $m^*=40$ (\ding{115}), $m^*=60$ (+) at Re 165 and $\zeta=0.1$. A reduction of maximum mean power can be observed when $m^*<40$. For $m^*>40$, the maximum power is essentially independent of $m^*$.}
    \label{fig:m_star_collapsed}
\end{figure}

Mean power as a function of damping factor at Re

>>>>

\setlength{\unitlength}{\textwidth}

  \begin{picture}(1,0.3)(0.0,0.45)

@@

  \end{picture}

  \caption{Mean power as a function of damping factor. Data are presented at $m^*=10$ (\ding{108}), $m^*=20$ (\ding{83}), $m^*=40$ (\ding{115}), $m^*=60$ (+) at Re 165 (a) with and (b) without the shedding term in Eq.\ref{final_equation_motion}. A reduction of maximum mean power can be observed when $m^*<40$ with shedding while the maximum power is essentially independent of $m^*$ when shedding is disregarded.}
    \label{fig:m_star_collapsed}
\end{figure}

### 2013-10-31 research/paper/figure/mstar_parkinson.tex
uploaded 31 OCt 2013

\begin{figure}
  \setlength{\unitlength}{\textwidth}
\fbox{
        \begin{picture}(1,0.3)(0.0,0.45)

@@

    \end{picture}
}
  \caption{}
    \label{fig:collpased_data}
\end{figure}

>>>>

\begin{figure}
  \setlength{\unitlength}{\textwidth}

        \begin{picture}(1,0.3)(0.0,0.45)

@@

    \end{picture}
  \caption{Mean power as a function of damping factor. Data presented in both (a) and (b) were calculated using input data at \reynoldsnumber=22300 \cite{Parkinson1964} where (a) shows mean power data at six different mass ratios: $m^*=1164$ (\ding{83}), $m^*=100$ (\ding{116}), $m^*=50$ (\ding{108}), $m^*=10$ (+), $m^*=5$ (\ding{110}) and $m^*=1$ ($\times)$ at \ustar=175. Data presented in (b) shows mean power data at three different reduced velocities: \ustar=75 (\ding{108}), \ustar=175 (\ding{83}) and \ustar=375 (\ding{116}) and \ustar=375 (\ding{83}) at $m^*=10$. The maximum mean power tend to increase with decreasing $m^*$ as well as increasing \ustar at low $m^*$.}

    \label{fig:mstarcollapsed_parkinson}
\end{figure}

### 2013-10-31 research/paper/results/results-2.3.tex
uploaded 22-oct 2013 6.36
uploaded 31 OCt 2013

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig. \ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq < 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at low incident angles. In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.

@@

 \input{../figure/m_star_collapsed}

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced. When the galloping excitation is suppressed at low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding. This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$. The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_d$ in Fig.\ref{fig:power_time_histories}. While the time average of both quantities are the same, instantaneously they are not. Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle. In cases where $m^*$ is very low, the system lack adequate inertia to store this power which leads to suppression of galloping.

>>>>

 At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.\ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.  The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq < 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal. In this case, power output is limited by the low fluid forces present at low incident angles. In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.

@@

 \input{../figure/m_star_collapsed}
 \input{../figure/mstar_parkinson}

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced. However, when the sinusoidal forcing function in Eq.\ref{equationofmotion} which cater for the vortex shedding was disregarded, the reduction in power could not be observed Fig.\ref{fig:m_star_collapsed}(b). An influence of vortex shedding on power is present. This maybe dude to the reduction in inertia as the mass ratio is decreased.

At \reynoldsnumber=22300 two major phenomena was present. The maximum of the mean power tend to increase  as the $m^*$ was decreased while keeping the $U^*$ constant (Fig\ref{fig:mstarcollapsed_parkinson}(a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson}(b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios Fig.\ref{time_history_mstar} and \ref{time_history_mstar} shows that essentially the same \hilight{phenomenon} occurring in both cases whereby the velocity signal tend to move towards a square from a sinusoidal signal.

\input{../figure/time_history_msar_mass}

\input{../figure/time_history_msar_ustar}
